Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola

### 2022-07-29 Manuscript/main.tex
Worked on manuscript

%\newcounter{captionedequationset} %numbering
%\newdimen\captionlength
%\newcommand{\captionedequationset}[1]{
%    \refstepcounter{captionedequationset}% Step counter
%    \setlength{\captionlength}{\widthof{#1}} %
%    \addtolength{\captionlength}{\widthof{Equation set~\thecaptionedequationset: }}
%    %If the caption is shorter than the line width then
%    % the caption is centred, otherwise is flushed left.
%    \ifthenelse{\lengthtest{\captionlength < \linewidth }} %
%    {\begin{center}
%            Equation set~\thecaptionedequationset: #1
%        \end{center}} 
%    { \begin{flushleft} 
%        Equation set~\thecaptionedequationset: #1 %
%        \end{flushleft}}
%}

@@

\subsection{Analysis}
To examine how yield is influenced by visitation, we used piecewise structural equation models (pSEM, \citealp{shipley2009}).
Structural equation models are a set of linear models arranged in a causal network, which provides a framework for testing hypotheses about complex systems \citep{grace2012, lefcheck2015}.
Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed yield within a causal framework (Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).
These models let us model how visitation ultimately influences seed yield, while controlling for other confounding factors (e.g. distance into field, measurements taken at different fields).
Pod set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from pod set to flower production as the closest approximation of this process.
The direction of the path could be reversed, implying that large flower production reduces the proportion of pod set, but we considered only the first scenario, as \citet{sabbahi2006} showed that low pod set increases flower production.

The underlying models of each pSEM were specified as generalized linear mixed-effects models (GLMMs, see Equation sets S1 and S2 for model specifications).
GLMMs can model processes that occur at different levels; for example, seed size was modelled at the plant level, while pollen deposition was modeled at the flower level.
% Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
Random intercepts were used to model variance at the field level and plot level, but plot-level variance terms had poor traces and low effective sample sizes, indicating low variation within plots.
Therefore, we omitted plot-level random effects for the commodity field models of pollen deposition, flower survival, seeds per pod, and seed size, and omitted them from the seed field models of seeds per pod and seed size.
% Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (LCB visits) with a log-link function. (Move to appendix)
Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay identity was excluded from further analysis.
% Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
% Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for LCB visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).

@@

Honey bee visitation decreased with distance away from the apiary, in both commodity and seed canola fields.
In commodity fields, honey bee visitation decreased from 6.4 visits/hr at the edge to 1.0 visits/hr at the centre of the field (400 m) (p$=$0.0002, Figure \ref{fig:allVis}, apiary of 40 hives).
% Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015. % (at a stocking level of 20 hives). 
Higher stocking rates increased honey bee visitation at the edge of the field from 3.9 visits/hr with an apiary of 20 hives, increasing to 6.4 visits/hr with 40 hives (Z=5.3, p$<$0.0001), while unstocked field edges had an average of 0.4 visits/hr.
Honey bee visitation was much higher overall in seed canola fields, and decreased from 99.5 visits/hr at edge to 78.8 visits/hr at the centre of the field (Z=-2.5, p$=$0.01). 
Honey bee visitation was also lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with LCBs (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).

LCB visitation declined rapidly with distance from the nearest shelter, showing visitation rates of 350 visits/hr at 2 m declining to 83 visits/hr at 10 m (Z=-11.4, p$=$0.0001). 
Surprisingly, LCB visitation was also higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
% However, there was no difference in visitation rates between the edge and the centre when leafcutter cocoon stocking was lower (Z=2.2, p$=$0.028), indicating that leafcutters at high stocking densities likely aggregate in shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
% There was no difference in visitation rates between the male bay and the edge of the female bays (LCB: p$=$0.72, honey bee: p$=$0.32). 
LCB visitation was also lower in the centre of the female bays (p$=$0.04, 51 vs. 29 visits/hr), while honey bee visitation was higher (p$=$0.008, 71 vs. 117 visits/hr, Figure \ref{fig:edgeCentVis_both}), indicating that pollination is likely done by different species in different parts of the field.
%Therefore, visitation by both species strongly decreases with distance from the edge of the field, decreases with distance from the leafcutter shelters in seed canola fields, and is done by different bees at the centre of the female bay.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allVisits.png}
    \caption{Effect of distance from a) honey bee apiaries, b) leafcutter shelters, and c) female bay position on visitation rates. Commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).}
    \label{fig:allVis}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{allPollen.png}
    \caption{Effect of a) visitation rate, b) distance from apiary (HB) or shelter (LCB), and c) female bay position on pollen deposition.}
    \label{fig:allPollen}
\end{figure}

@@

\begin{figure} 
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{plDensPlSize_both.png}
    \caption[Partial effects of plant density on plant size]{Partial effects of plant density on plant size, for commodity and seed canola plants. Solid lines represents median, and shaded areas represent 95\% CIs.}
    \label{fig:plDensPlSize}
\end{figure}

Plant size had by far the strongest positive effect on the number of pods produced, and there was evidence of pod set suppressing flower production.
Commodity canola plants produced fewer flowers (mean: 198, SD: 157, range: 13--1419) than seed canola plants (mean: 468, SD: 328, range: 26--2712), and also produced fewer pods per plant (mean: 143, SD: 114, range: 5--892 vs. mean: 303, SD: 208, range: 10--1410).
In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant (both p$<<$0.0001, Figure \ref{fig:plSizeFlwCount}), as well as pod set (both p$<$0.001, Figure \ref{fig:flwSurv_both}).
Pod set had a strong negative influence on total flowers per plant (p$<$0.0001) in both commodity and seed canola (both p$<<$0.0001), indicating that high pod set suppresses future flower production.
Finally, commodity plants were also lower-yielding (mean: 6.8 g of seeds per plant, SD: 6.0, range: 0.01--47.9) than seed canola plants (mean: 9.6, SD: 7.9, range: 0.02--60.8).
However, the harvest index of commodity canola (mean: 0.26, SD: 0.08, range: 0.005--0.65) was higher than seed canola (mean: 0.23, SD: 0.09, range: 0.003--0.55), meaning that commodity plants produced more seeds per gram of biomass than seed canola plants.%, likely due to the lack of pollen limitation.

\begin{figure} %SH: HARD TO COMPARE BECAUSE OF DIFFERENT AXES
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{plSizeflwCount_both.png}
    \caption[Partial effect of plant size on number of flowers per plant]{Partial effect of plant size on number of flowers per plant, for commodity and seed canola plants. Solid lines represent median, and shaded areas represent 95\% CIs.}
    \label{fig:plSizeFlwCount}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{plSizeFlwSurv_both.png} 
    \caption[Partial effect of plant size on pod set]{Partial effect of plant size on pod set (\% of flowers that became pods), for both commodity and seed canola. Solid lines represent median, and shaded areas represent 95\% CIs.}
    \label{fig:flwSurv_both}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{seedWeightSeedCount_both.png}
    \caption[Partial effects of seed count and plant size on seed size]{Partial effects of seed count and plant size on seed size, for both commodity and seed canola. Solid lines represent median, and shaded areas represent 95\% CIs.}
    \label{fig:seedWeightCount_both}
\end{figure}

@@

%Leafcutter-honeybee interactions
Honey bee visitation in hybrid seed fields was lower at areas near to leafcutter shelters. 
This may have been driven by avoidance of nectar and pollen competition near shelters, as areas close to leafcutter shelters may become depleted in nectar and pollen, deterring honey bee visitation (similar to \citealp{currie1997}).
Honey bees also suffer from direct interference by LCBs near to their shelters.
Several times during the study, \textit{M. rotundata} females and males directly harassed honey bees during the plot-level observations, tackling honey bees both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytesMsc}). 
Honey bees were never the aggressor in these interactions, so interference between LCBs and honey bees may be unidirectional, at least in areas near LCB shelters. 
For this reason, we treated high leafcutter visitation as causing lower honey bee visitation in our SEM (Figure \ref{fig:seedSEM}, arrow from leafcutter visit rate to honey bee visit rate).

@@

%REVIEW THIS
Honey bee behaviour in seed fields made pollen transfer between male and female plants unlikely, and this was also reflected in the measurements of stigma deposition. 
Deposition was not affected by honey bee visitation, but was strongly increased by LCB visitation.
LCBs tend to switch between male and female flowers more frequently than honey bees do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers (\citealp{soroka2001}, personal observation), which may explain their increased pollination efficacy.
We also found that pollen deposition also decreased with distance from the edge of the field, was lower in the centre of the female bays, and that this was not solely explained by LCB abundance (Figure \ref{fig:seedSEM}).
During foraging bouts, LCBs may travel further between flowers than honey bees do; \citet{brunet2019} found that LCBs foraging in alfalfa (\emph{Medicago sativa} L.) travelled an average of 21 cm between flowers, while honey bees only travelled 16 cm.
However, pollen carryover \citep{thomson1986} to the middle of the bay female is likely reduced, as leafcutters likely visit the edge of the female bay before venturing into the centre.
The decrease of pollen deposition with distance into the field (independent of visitation rates) also suggests that the same visitation rate of pollinators in the centre of the field results in less pollen deposition.
This may be due to lower levels of competition at the centre of the field, leading to a higher nectar (or pollen) standing crop. %LH: more likely that bees at centre of F bays carry less pollen
Foraging \textit{Bombus} take smaller trips between flowers and will forage in smaller areas under nectar-rich conditions (area-restricted search, \citealp{pyke1978b, heinrich1979}), so leafcutter foraging may follow a similar pattern, causing lower pollen deposition at the centre of the field where competition is lower.
%LCBs are extremely fast fliers, and are difficult to follow after they leave an inflorescence, meaning that tracking their movements during an entire foraging bout would be almost impossible.
% Visits by honey bee foragers were almost twice as high in the centre of the female bay, but pollen deposition was about 40\% lower (  Figure \ref{fig:distCentPol}), which correspondingly is 
% Honey bees in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower (Figure \ref{fig:distCentPol}).
% While we found that LCBs also tend to avoid the centre of the female bays, and decrease with distance into the field, this extra dependence could have been caused by the fact that the visitation data represents a short ``snapshot'' of the pollen deposition process.
% For example, canola flowers are receptive for 1-2 days before the petals dehisce, while the surveys only recorded 5 or 10 minutes of visitation, meaning we may have not captured the deposition process on the time scale that it occurs, and the extra variance is being accounted for by distance from field edge and the centre of the female bay.
% Leafcutter visitation can be extremely sporadic, so the distance and bay position measurements capture differences in the average visitation process better than 10 minute measurements.
% Pollen deposition also likely changes over the course of the season, as flower availability decreases.

@@

%Seed size
Plant size was one of the dominant factors controlling seed size in seed canola, while in commodity canola, plant size did not influence seed size.
Plant size can positively influence seed size in some plant species \citep{maddox1983}, and this appears to be true in canola \citep{riffkin2012} as well as other Brassicaceae \citep{mazer1987}.
Similarly, seeds per pod and seed weight varied positively in commodity canola, this pattern was reversed in seed canola (Figure \ref{fig:seedWeightCount_both}). 
These differences likely occurred because of variation in available seed resources among the parts of the plant \citep{vanNoordwijk1986}, which can cause a positive size-number relationship even in resource-limited plants. 
In commodity canola, pollen is readily available, and there seems to be little difference between outcrossed- and self-pollen \citep{steffan2003, rosa2011}. 
Canola plants produce flowers from the bottom up, and produce fewer, smaller seeds at the ends of the branches because the younger pods have access to fewer resources at the end of the season \citep{sabbahi2006}, resulting in an increased rate of seed abortion \citep{clarke1979}.
Pods with low resources at the end of the season are forced to abort more ovules \citep{wang2011}, causing a positive relationship between seed number and size.
Thus, in commodity canola, variation in resources with plant size is masked by resource variation over time.  
In seed canola, pollen is much rarer (median: 7 grains/stigma vs. 155 in commodity), but plant sizes are similar (or larger) than commodity canola, such that plant resources are still available to developing pods at the end of the season.
This causes a size-number trade-off within pods that is mediated by plant size.
Most studies on commodity canola report a seed size-number trade-off at the level of plant \citep{angadi2003,koltowski2005}, we found a positive relationship at the pod level (but see \citealp{sabbahi2005}).
Perhaps within-plant resource variation is a more likely driver of seed number than pollen deposition, as pollination did not appear to be limiting (Figure \ref{fig:commoditySEM}, weak paths from pollen to yield metrics).
%While we did not quantify pod position on branches, the pods at the end of the branches did appear to have fewer seeds, meaning that some of the variation within plants likely occurred because of late-season seed.
%Why did the same species of plant experience such different relationships between seed size and seed number, and such different effects of plant size (a proxy of resource availability)?
%Because of this abundance of pollen, resource availability decreases over time as the plant matures ovules into seeds, becoming restricted at the end of the season.
% Ovule abortion in \textit{Brassica} is also higher at the beginning and end of the flowering season, likely because of a lower amount of high-quality pollen available at the tails of the season \citep{wang2011}.
% Similarly, the main raceme of canola tends to produce the most seeds per pod, with accessory branches producing fewer, smaller seeds, again due to flowers on branches being produced later in the season than the flowers on the main raceme \citep{clarke1979}.

>>>>

%\newcounter{captionedequationset} %numbering
%\newdimen\captionlength
%\newcommand{\captionedequationset}[1]{
%    \refstepcounter{captionedequationset}% Step counter
%    \setlength{\captionlength}{\widthof{#1}} %
%    \addtolength{\captionlength}{\widthof{Equation set~\thecaptionedequationset: }}
%    %If the caption is shorter than the line width then
%    % the caption is centred, ot is flushed left.
%    \ifthenelse{\lengthtest{\captionlength < \linewidth }} %
%    {\begin{center}
%            Equation set~\thecaptionedequationset: #1
%        \end{center}} 
%    { \begin{flushleft} 
%        Equation set~\thecaptionedequationset: #1 %
%        \end{flushleft}}
%}

@@

\subsection{Analysis}
To examine how yield is influenced by visitation, we used piecewise structural equation models (pSEM, \citealp{shipley2009}).
Structural equation models are a set of linear models arranged in a causal network, which provides a framework for testing hypotheses about complex systems \citep{grace2012, lefcheck2015}.
Starting with a simple model (visitation $\rightarrow$ pollen deposition $\rightarrow$ fruit production $\leftarrow$ plant resources), we built a detailed model relating visitation to pollination to seed yield within a causal framework (see Figure \ref{fig:allSEM} in Results).
These models let us model how visitation ultimately influences seed yield, while controlling for other confounding factors (e.g. distance into field, measurements taken at different fields).
Pod set can suppress future vegetative growth and flower production \citep{stephenson1981}, but SEMs do not allow for causal loops \citep{grace2012}, so we included a path from pod set to flower production as the closest approximation of this process.
The direction of the path could be reversed, implying that large flower production reduces the proportion of pod set, but we considered only the first scenario, as \citet{sabbahi2006} showed that low pod set increases flower production.

The underlying models of each pSEM were specified as generalized linear mixed-effects models (GLMMs, see Equation sets S1 and S2 for model specifications).
GLMMs can model processes that occur at different levels; for example, seed size was modelled at the plant level, while pollen deposition was modeled at the flower level.
% Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
Random intercepts were used to model variance at the field level and plot level, but plot-level variance terms had poor traces and low effective sample sizes, indicating low variation within plots.
Therefore, we omitted plot-level random effects for the commodity field models of pollen deposition, flower survival, seeds per pod, and seed size, and omitted them from the seed field models of seeds per pod and seed size.
% Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (LCB visits) with a log-link function. (Move to appendix)
Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay identity was excluded from further analysis.
% Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
% Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for LCB visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:allSEM} and \ref{fig:allSEM}).

@@

Honey bee visitation decreased with distance away from the apiary, in both commodity and seed canola fields.
In commodity fields, honey bee visitation decreased from 6.4 visits/hr at the edge to 1.0 visits/hr at the centre of the field (400 m) (p$=$0.0002, Figure \ref{fig:allVisits}, apiary of 40 hives).
% Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015. % (at a stocking level of 20 hives). 
Higher stocking rates increased honey bee visitation at the edge of the field from 3.9 visits/hr with an apiary of 20 hives, increasing to 6.4 visits/hr with 40 hives (Z=5.3, p$<$0.0001), while unstocked field edges had an average of 0.4 visits/hr.
Honey bee visitation was much higher overall in seed canola fields, and decreased from 99.5 visits/hr at edge to 78.8 visits/hr at the centre of the field (Z=-2.5, p$=$0.01). 
Honey bee visitation was also lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with LCBs (Figure \ref{fig:allVisits}).

LCB visitation declined rapidly with distance from the nearest shelter, showing visitation rates of 350 visits/hr at 2 m declining to 83 visits/hr at 10 m (Z=-11.4, p$=$0.0001). 
Surprisingly, LCB visitation was also higher at the edge of the field than the centre (Z=-4.4, p$=$0.0001, 114 visits/hr vs 28 visits/hr).
% However, there was no difference in visitation rates between the edge and the centre when leafcutter cocoon stocking was lower (Z=2.2, p$=$0.028), indicating that leafcutters at high stocking densities likely aggregate in shelters close to the edge of the field (Figure \ref{fig:hbeeDist_both}).
% There was no difference in visitation rates between the male bay and the edge of the female bays (LCB: p$=$0.72, honey bee: p$=$0.32). 
LCB visitation was also lower in the centre of the female bays (p$=$0.04, 51 vs. 29 visits/hr), while honey bee visitation was higher (p$=$0.008, 71 vs. 117 visits/hr, Figure \ref{fig:allVisits}), indicating that pollination is likely done by different species in different parts of the field.
%Therefore, visitation by both species strongly decreases with distance from the edge of the field, decreases with distance from the leafcutter shelters in seed canola fields, and is done by different bees at the centre of the female bay.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allVisits.png}
    \caption{Effect of distance from a) honey bee apiaries, b) leafcutter shelters, and c) female bay position on visitation rates. Commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).}
    \label{fig:allVisits}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allPollen.png}
    \caption{Effect of a) visitation rate, b) distance from apiary (HB) or shelter (LCB), and c) female bay position on pollen deposition.}
    \label{fig:allPollen}
\end{figure}

@@

Plant size had by far the strongest positive effect on the number of pods produced, and there was evidence of pod set suppressing flower production.
Commodity canola plants produced fewer flowers (mean: 198, SD: 157, range: 13--1419) than seed canola plants (mean: 468, SD: 328, range: 26--2712), and also produced fewer pods per plant (mean: 143, SD: 114, range: 5--892 vs. mean: 303, SD: 208, range: 10--1410).
In both commodity and seed canola, plant size had a strong positive effect on the total number of flowers per plant as well as pod set (both p$<$0.001).
Pod set had a strong negative influence on total flowers per plant (p$<$0.0001) in both commodity and seed canola (both p$<<$0.0001), indicating that high pod set suppresses future flower production.
Finally, commodity plants were also lower-yielding (mean: 6.8 g of seeds per plant, SD: 6.0, range: 0.01--47.9) than seed canola plants (mean: 9.6, SD: 7.9, range: 0.02--60.8).
However, the harvest index of commodity canola (mean: 0.26, SD: 0.08, range: 0.005--0.65) was higher than seed canola (mean: 0.23, SD: 0.09, range: 0.003--0.55), meaning that commodity plants produced more seeds per gram of biomass than seed canola plants.%, likely due to the lack of pollen limitation.

@@

@@

%Leafcutter-honeybee interactions
Honey bee visitation in hybrid seed fields was lower at areas near to leafcutter shelters. 
This may have been driven by avoidance of nectar and pollen competition near shelters, as areas close to leafcutter shelters may become depleted in nectar and pollen, deterring honey bee visitation (similar to \citealp{currie1997}).
Honey bees also suffer from direct interference by LCBs near to their shelters.
Several times during the study, \textit{M. rotundata} females and males directly harassed honey bees during the plot-level observations, tackling honey bees both on the flowers and in the air (also seen by \citealp{batra1978} and \citealp{waytesMsc}). 
Honey bees were never the aggressor in these interactions, so interference between LCBs and honey bees may be unidirectional, at least in areas near LCB shelters. 
For this reason, we treated high leafcutter visitation as causing lower honey bee visitation in our SEM (Figure \ref{fig:allSEM}, arrow from leafcutter visit rate to honey bee visit rate).

@@

%REVIEW THIS
Honey bee behaviour in seed fields made pollen transfer between male and female plants unlikely, and this was also reflected in the measurements of stigma deposition. 
Deposition was not affected by honey bee visitation, but was strongly increased by LCB visitation.
LCBs tend to switch between male and female flowers more frequently than honey bees do \citep{waytesMsc}, transport more viable pollen between flowers \citep{parker2015}, and tend not to side-work canola flowers (\citealp{soroka2001}, personal observation), which may explain their increased pollination efficacy.
We also found that pollen deposition also decreased with distance from the edge of the field, was lower in the centre of the female bays, and that this was not solely explained by LCB abundance (Figure \ref{fig:allSEM}).
During foraging bouts, LCBs may travel further between flowers than honey bees do; \citet{brunet2019} found that LCBs foraging in alfalfa (\emph{Medicago sativa} L.) travelled an average of 21 cm between flowers, while honey bees only travelled 16 cm.
However, pollen carryover \citep{thomson1986} to the middle of the bay female is likely reduced, as leafcutters likely visit the edge of the female bay before venturing into the centre.
The decrease of pollen deposition with distance into the field (independent of visitation rates) also suggests that the same visitation rate of pollinators in the centre of the field results in less pollen deposition.
This may be due to lower levels of competition at the centre of the field, leading to a higher nectar (or pollen) standing crop. %LH: more likely that bees at centre of F bays carry less pollen
Foraging \textit{Bombus} take smaller trips between flowers and will forage in smaller areas under nectar-rich conditions (area-restricted search, \citealp{pyke1978b, heinrich1979}), so leafcutter foraging may follow a similar pattern, causing lower pollen deposition at the centre of the field where competition is lower.
%LCBs are extremely fast fliers, and are difficult to follow after they leave an inflorescence, meaning that tracking their movements during an entire foraging bout would be almost impossible.
% Visits by honey bee foragers were almost twice as high in the centre of the female bay, but pollen deposition was about 40\% lower (  Figure \ref{fig:distCentPol}), which correspondingly is 
% Honey bees in seed fields tended to visit more in the centre of the female bay, even close to the edge of the field, yet pollen deposition was still about 40\% lower (Figure \ref{fig:distCentPol}).
% While we found that LCBs also tend to avoid the centre of the female bays, and decrease with distance into the field, this extra dependence could have been caused by the fact that the visitation data represents a short ``snapshot'' of the pollen deposition process.
% For example, canola flowers are receptive for 1-2 days before the petals dehisce, while the surveys only recorded 5 or 10 minutes of visitation, meaning we may have not captured the deposition process on the time scale that it occurs, and the extra variance is being accounted for by distance from field edge and the centre of the female bay.
% Leafcutter visitation can be extremely sporadic, so the distance and bay position measurements capture differences in the average visitation process better than 10 minute measurements.
% Pollen deposition also likely changes over the course of the season, as flower availability decreases.

@@

%Seed size
Plant size was one of the dominant factors controlling seed size in seed canola, while in commodity canola, plant size did not influence seed size.
Plant size can positively influence seed size in some plant species \citep{maddox1983}, and this appears to be true in canola \citep{riffkin2012} as well as other Brassicaceae \citep{mazer1987}.
Similarly, seeds per pod and seed weight varied positively in commodity canola, this pattern was reversed in seed canola (Figure \ref{fig:seedWeightCount_both}). 
These differences likely occurred because of variation in available seed resources among the parts of the plant \citep{vanNoordwijk1986}, which can cause a positive size-number relationship even in resource-limited plants. 
In commodity canola, pollen is readily available, and there seems to be little difference between outcrossed- and self-pollen \citep{steffan2003, rosa2011}. 
Canola plants produce flowers from the bottom up, and produce fewer, smaller seeds at the ends of the branches because the younger pods have access to fewer resources at the end of the season \citep{sabbahi2006}, resulting in an increased rate of seed abortion \citep{clarke1979}.
Pods with low resources at the end of the season are forced to abort more ovules \citep{wang2011}, causing a positive relationship between seed number and size.
Thus, in commodity canola, variation in resources with plant size is masked by resource variation over time.  
In seed canola, pollen is much rarer (median: 7 grains/stigma vs. 155 in commodity), but plant sizes are similar (or larger) than commodity canola, such that plant resources are still available to developing pods at the end of the season.
This causes a size-number trade-off within pods that is mediated by plant size.
Most studies on commodity canola report a seed size-number trade-off at the level of plant \citep{angadi2003,koltowski2005}, we found a positive relationship at the pod level (but see \citealp{sabbahi2005}).
Perhaps within-plant resource variation is a more likely driver of seed number than pollen deposition, as pollination did not appear to be limiting (Figure \ref{fig:allSEM}, weak paths from pollen to yield metrics).
%While we did not quantify pod position on branches, the pods at the end of the branches did appear to have fewer seeds, meaning that some of the variation within plants likely occurred because of late-season seed.
%Why did the same species of plant experience such different relationships between seed size and seed number, and such different effects of plant size (a proxy of resource availability)?
%Because of this abundance of pollen, resource availability decreases over time as the plant matures ovules into seeds, becoming restricted at the end of the season.
% Ovule abortion in \textit{Brassica} is also higher at the beginning and end of the flowering season, likely because of a lower amount of high-quality pollen available at the tails of the season \citep{wang2011}.
% Similarly, the main raceme of canola tends to produce the most seeds per pod, with accessory branches producing fewer, smaller seeds, again due to flowers on branches being produced later in the season than the flowers on the main raceme \citep{clarke1979}.

### 2022-07-29 Manuscript/visitors_supplemental.tex
Worked on manuscript

\begin{table}[h]
    \begin{tabular}{r|r|l|r|l}
     & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c}{Seed fields} \\ \cline{2-5}
    Taxon & Visits & \% & Visits & \% \\ \hline
    Honey bee & 470 & 53.5 & 4850 & 77.1 \\
    Fly & 222 & 25.3 & 74 & 0.878 \\
    Hover fly & 94 & 10.7 & 151 & 1.79 \\
    Other bee & 47 & 5.35 & 30 & 0.356 \\
    Bumble bee & 25 & 2.85 & 0 & 0 \\
    Butterfly & 16 & 1.82 & 0 & 0 \\
    Leafcutter bee & 4 & 0.456 & 1675 & 19.9 \\
    % \hline
    % Total & 828 & - & 6780 & - \\
    \end{tabular}
    \caption[Flower visiting insects observed in commodity and seed canola fields]{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016). ``Fly" refers to larger calyptrate muscoid flies (families Muscidae, Anthomyiidae, Caliphoridae), while ``Hover fly" refers to Syrphid flies. ``Other bee" included Halictid and Andrenid bees, while ``Bumble bee" was \textit{Bombus} spp. ``Butterfly" refers to all visiting Lepidopterans, mostly Pierids.}
    \label{tab:propVisitors}  
\end{table}

>>>>

\begin{table}[h]
    \begin{tabular}{r|r|l|r|l}
     & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c}{Seed fields} \\ \cline{2-5}
    Taxon & Visits & \% & Visits & \% \\ \hline
    Honey bee & 470 & 53.5 & 4850 & 77.1 \\
    Fly & 222 & 25.3 & 74 & 0.878 \\
    Hover fly & 94 & 10.7 & 151 & 1.79 \\
    Other bee & 47 & 5.35 & 30 & 0.356 \\
    Bumble bee & 25 & 2.85 & 0 & 0 \\
    Butterfly & 16 & 1.82 & 0 & 0 \\
    Leafcutter bee & 4 & 0.456 & 1675 & 19.9 \\
    % \hline
    % Total & 828 & - & 6780 & - \\
    \end{tabular}
    \caption{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016). ``Fly" refers to larger calyptrate muscoid flies (families Muscidae, Anthomyiidae, Caliphoridae), while ``Hover fly" refers to Syrphid flies. ``Other bee" included Halictid and Andrenid bees, while ``Bumble bee" was \textit{Bombus} spp. ``Butterfly" refers to all visiting Lepidopterans, mostly Pierids.}
    \label{tab:propVisitors}  
\end{table}
